Analysis of observational data, to calculate the Delayed-Tau model parameters

### 2025-02-06 thesis.qmd
figure->images

![Star Formation Rate over the time of star formation, for different parametric models](figure/sfr-models.png){fig-align="center" width="300"}

@@

![The history of cosmic star formation as shown in @madauCosmicStarFormation2014](figure/lily-madau.png){fig-align="center" width="450"}

@@

![Scatter plot and the residuals of the $\text{mean}(SFR_{FUV},SFR_{H\alpha})$ from the UNGC catalog and the $SFR_{TIR}$. The SFR estimation from the FUV and H$\alpha$ is systematically lower than the $SFR_{TIR}$ estimator as expected. The $R^2$ is smaller than 80% however due to $\overline{\text{Residuals}}=0$ we can assume that the quantities are comparable.](images/paste-1.png){#fig-SFR-comparison width="60%"}

>>>>

![Star Formation Rate over the time of star formation, for different parametric models](images/sfr-models.png){fig-align="center" width="300"}

@@

![The history of cosmic star formation as shown in @madauCosmicStarFormation2014](images/lily-madau.png){fig-align="center" width="450"}

@@

![Scatter plot and the residuals of the $\text{mean}(SFR_{FUV},SFR_{H\alpha})$ from the UNGC catalog and the $SFR_{TIR}$. The SFR estimation from the FUV and H$\alpha$ is systematically lower than the $SFR_{TIR}$ estimator as expected. The $R^2$ is smaller than 80% however due to $\overline{\text{Residuals}}=0$ we can assume that the quantities are comparable.](compare/quickplots/SFR.png){#fig-SFR-comparison width="60%"}
